Predicting information integration in pragmatic word learning across development

### 2021-01-05 papers/full_paper/models.Rmd
add updated model file
add flat prior dev noise
add child prior only model llh
prep for re-submission

ggplot(ex3_noise_parameters, aes(x = value, col = model, fill = model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlim(0,1)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))
```

@@

```{r plot ex3 model predictions and data adults, include = T}
ggplot(data = ex_3_pred, aes(x = alignment, y = mean, col = model)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion more informative")+
  facet_grid (~ common_ground_manipulation + speaker) +
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_manual(name="Model",
                     breaks=c("data","pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
                     values= c("black","#859900","#00afaf","#6c71c4","#b58900"))+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
```

@@

```{r likelihood plot adults, include = T}
ggplot(ex3_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=logP, yend=0), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  scale_color_manual(breaks=c("pragmatic","pragmatic_noise","prior_only_noise","flat_prior_noise"),
                    values= c("#00afaf","#b58900","#859900","#6c71c4"))
```

@@

ggplot(ex4_noise_parameters, aes(x = value, col = model, fill = model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlim(0,1)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))
```

@@

```{r plot ex4 model predictions and data adults, include = T}
ggplot(data = ex_4_pred, aes(x = alignment, y = mean, col = model)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion more informative")+
  facet_grid ( prior_manipulation ~ common_ground_manipulation + speaker) +
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_manual(name="Model",
                     breaks=c("data","pragmatic_noise","flat_prior_noise","prior_only_noise"),
                     values= c("black","#b58900","#6c71c4","#859900"))+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))

@@

```{r plot for loglikelihood ex4 adults, include = T}
ggplot(ex4_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=logP, yend=0), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#859900","#b58900","#6c71c4"))
```

@@

```{r predictions pragmatic model ex3 children}
child_ex3_pragm_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR"
)

# model predictions
child_ex3_pragm_model_predictions <- child_ex3_pragm_model %>%
  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
  mutate(mean = `1`,
         ci_lower = mean,
         ci_upper = mean,
         model="pragmatic",
         age = as.numeric(age))%>%
  select(-`1`)
```

@@

ggplot(child_noise_parameters, aes(x = value, col = model, fill = model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlim(0,1)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))
```

@@

ggplot(developmental_noise_parameter, aes(x = age, y= y, col = model))+
  geom_line(size = 1)+
  ylab("Noise parameter")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#b58900","#6c71c4","#859900"))
```

@@

child_ex3_pragm_model_likelihood_marginal <- child_ex3_pragm_model_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))

@@

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_prag_noise.csv")%>%
  mutate(model = "pragmatic",
         parameter = "noise")%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")

@@

child_ex3_pragm_model_noise_likelihood_marginal <- child_ex3_pragm_model_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))
```

@@

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_prag_dev_noise.csv")%>%
  mutate(model = "pragmatic",
         parameter = "developmental noise")%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")

@@

child_ex3_pragm_model_developmental_noise_likelihood_marginal <- child_ex3_pragm_model_developmental_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))

@@

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_flat_prior_param_free.csv")%>%
  mutate(model = "flat_prior",
         parameter = "parameter free")%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")

@@

child_ex3_flat_prior_model_likelihood_marginal <- child_ex3_flat_prior_model_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))

@@

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_flat_prior_noise.csv")%>%
  mutate(model = "flat_prior",
         parameter = "noise")%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")

@@

child_ex3_flat_prior_model_noise_likelihood_marginal <- child_ex3_flat_prior_model_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))

@@

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_flat_prior_dev_noise.csv")%>%
  mutate(model = "flat_prior",
         parameter = "developmental noise")%>%
  saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")

@@

child_ex3_flat_prior_model_developmental_noise_likelihood_marginal <- child_ex3_flat_prior_model_developmental_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))
```

@@

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.marginal.likelihood, sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_prior_only_param_free.csv")%>%
  mutate(model = "prior_only",
         parameter = "parameter free")%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")

@@

child_ex3_prior_only_model_likelihood_marginal <- child_ex3_prior_only_model_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))
```

@@

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood, sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_prior_only_noise.csv")%>%
  mutate(model = "prior_only",
         parameter = "noise")%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")

child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")

child_ex3_prior_only_model_noise_likelihood_marginal <- child_ex3_prior_only_model_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))
```

@@

```{r}
webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood, sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR",
  packages ="webppl-csv",
  chains = 1,
  cores = 1
)

read_csv("../../stats/data/llh_child_prior_only_dev_noise.csv")%>%
  mutate(model = "prior_only",
         parameter = "developmental noise")%>%
  saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")

@@

child_ex3_prior_only_model_developmental_noise_likelihood_marginal <- child_ex3_prior_only_model_developmental_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight))

@@

child_ex3_model_comparison <- bind_rows(
  child_ex3_pragm_model_likelihood_marginal,
  child_ex3_pragm_model_noise_likelihood_marginal,
  child_ex3_pragm_model_developmental_noise_likelihood_marginal,
  child_ex3_flat_prior_model_noise_likelihood_marginal,
  child_ex3_flat_prior_model_likelihood_marginal,
  child_ex3_flat_prior_model_developmental_noise_likelihood_marginal,
  child_ex3_prior_only_model_noise_likelihood_marginal,
  child_ex3_prior_only_model_likelihood_marginal,
  child_ex3_prior_only_model_developmental_noise_likelihood_marginal
)%>%
  ungroup()%>%
  mutate(model = reorder(model,logP))%>%
  saveRDS("../../stats/saves/child_ex3_model_comparison.rds")

@@

#### Means
```{r plot model loglikes ex3 children, include = T}
ggplot(child_ex3_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=-400, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  facet_grid(~parameter)+
  ylim(-550,-400)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#859900","#b58900","#6c71c4"))

@@

```{r}
child_ex3_model_ll_dist <- bind_rows(
  child_ex3_pragm_model_likelihood,
  child_ex3_pragm_model_noise_likelihood,
  child_ex3_pragm_model_developmental_noise_likelihood,
  child_ex3_flat_prior_model_noise_likelihood,
  child_ex3_flat_prior_model_likelihood,
  child_ex3_flat_prior_model_developmental_noise_likelihood,
  child_ex3_prior_only_model_noise_likelihood,
  child_ex3_prior_only_model_likelihood,
  child_ex3_prior_only_model_developmental_noise_likelihood
)%>%
  ungroup()%>%
  mutate(model = reorder(model,weight))

ggplot(child_ex3_model_ll_dist, aes(x = weight, col = model, fill = model))+
  geom_histogram(alpha = .5)+
  facet_wrap(~parameter)+
  theme_few()+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#859900","#b58900","#6c71c4"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#859900","#b58900","#6c71c4"))

@@

```{r, include = T}
child_ex3_pragmatic_models_bf <- child_ex3_model_comparison%>%
  filter(model == "pragmatic")%>%
  spread(parameter, logP) %>%
  mutate("dev. noise > noise" = exp(`developmental noise` - noise),
         "noise > parameter free" = exp(noise - `parameter free`),
         "dev. noise > parameter free" = exp(`developmental noise` - `parameter free`)) %>%
  select(-`parameter free`,-`developmental noise`, -noise)

@@

```{r bayes factors ex3 children, include = T}
child_ex3_bf <- child_ex3_model_comparison%>%
  group_by(parameter)%>%
  spread(model, logP) %>%
  mutate("pragmatic > flat_prior" = exp(pragmatic - flat_prior),
         "pragmatic > prior_only" = exp(pragmatic - prior_only),
         "flat_prior > prior_only" = exp(flat_prior - prior_only)) %>%
  select(-pragmatic,-flat_prior, -prior_only)

>>>>

ggplot(ex3_noise_parameters, aes(x = value, col = model, fill = model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlim(0,1)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

```{r plot ex3 model predictions and data adults, include = T}
ggplot(data = ex_3_pred, aes(x = alignment, y = mean, col = model)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion more informative")+
  facet_grid (~ common_ground_manipulation + speaker) +
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_manual(name="Model",
                     breaks=c("data","pragmatic","pragmatic_noise","flat_prior_noise","prior_only_noise"),
                     values= c("black","#859900","#C5D86D","#86615C","#AFE0CE"))+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))
```

@@

```{r likelihood plot adults, include = T}
ggplot(ex3_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=logP, yend=0), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  scale_color_manual(breaks=c("pragmatic","pragmatic_noise","prior_only_noise","flat_prior_noise"),
                    values= c("#00afaf","#C5D86D","#86615C","#AFE0CE"))
```

@@

ggplot(ex4_noise_parameters, aes(x = value, col = model, fill = model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlim(0,1)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

```{r plot ex4 model predictions and data adults, include = T}
ggplot(data = ex_4_pred, aes(x = alignment, y = mean, col = model)) +
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper), size = .4,  position = position_dodge(width = .5), pch = 5)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion more informative")+
  facet_grid ( prior_manipulation ~ common_ground_manipulation + speaker) +
  theme_few() + 
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  scale_color_manual(name="Model",
                     breaks=c("data","pragmatic_noise","flat_prior_noise","prior_only_noise"),
                     values= c("black","#C5D86D","#86615C","#AFE0CE"))+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))

@@

```{r plot for loglikelihood ex4 adults, include = T}
ggplot(ex4_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=logP, yend=0), col = "black", size = 1)+
  geom_point(size = 7)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

```{r predictions pragmatic model ex3 children}
child_ex3_pragm_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.predictions , sep='\n'),
  data =list(allData = ex3_model_data),
  data_var = "dataFromR"
)%>%
  saveRDS("../../stats/saves/child_ex3_pragm_model.rds")

# model predictions
child_ex3_pragm_model_predictions <- readRDS("../../stats/saves/child_ex3_pragm_model.rds") %>%
  separate(`0`, into = c("age", "speaker", "alignment","correct"), sep="/")%>%
  mutate(mean = `1`,
         ci_lower = mean,
         ci_upper = mean,
         model="pragmatic",
         age = as.numeric(age))%>%
  select(-`1`)
```

@@

ggplot(child_noise_parameters, aes(x = value, col = model, fill = model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlim(0,1)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

ggplot(developmental_noise_parameter, aes(x = age, y= y, col = model))+
  geom_line(size = 1)+
  ylab("Noise parameter")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

child_ex3_pragm_model_likelihood_marginal <- child_ex3_pragm_model_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight),
            ci_lower = hdi_lower(weight),
            ci_upper = hdi_upper(weight))

@@

```{r}
# webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   packages ="webppl-csv",
#   chains = 1,
#   cores = 1
# )
# 
# read_csv("../../stats/data/llh_child_prag_noise.csv")%>%
#   mutate(model = "pragmatic",
#          parameter = "noise")%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model_noise_loglike.rds")

@@

child_ex3_pragm_model_noise_likelihood_marginal <- child_ex3_pragm_model_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight),
            ci_lower = hdi_lower(weight),
            ci_upper = hdi_upper(weight))
```

@@

```{r}
# webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.rsa.developmental.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   packages ="webppl-csv",
#   chains = 1,
#   cores = 1
# )
# 
# read_csv("../../stats/data/llh_child_prag_dev_noise.csv")%>%
#   mutate(model = "pragmatic",
#          parameter = "developmental noise")%>%
#   saveRDS("../../stats/saves/child_ex3_pragm_model_developmenatl_noise_loglike.rds")

@@

child_ex3_pragm_model_developmental_noise_likelihood_marginal <- child_ex3_pragm_model_developmental_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight),
            ci_lower = hdi_lower(weight),
            ci_upper = hdi_upper(weight))

@@

```{r}
# webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   packages ="webppl-csv",
#   chains = 1,
#   cores = 1
# )
# 
# read_csv("../../stats/data/llh_child_flat_prior_param_free.csv")%>%
#   mutate(model = "flat_prior",
#          parameter = "parameter free")%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_loglike.rds")

@@

child_ex3_flat_prior_model_likelihood_marginal <- child_ex3_flat_prior_model_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight),
            ci_lower = hdi_lower(weight),
            ci_upper = hdi_upper(weight))

@@

```{r}
# webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   packages ="webppl-csv",
#   chains = 1,
#   cores = 1
# )
# 
# read_csv("../../stats/data/llh_child_flat_prior_noise.csv")%>%
#   mutate(model = "flat_prior",
#          parameter = "noise")%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_noise_loglike.rds")

@@

child_ex3_flat_prior_model_noise_likelihood_marginal <- child_ex3_flat_prior_model_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight),
            ci_lower = hdi_lower(weight),
            ci_upper = hdi_upper(weight))

@@

```{r}
# webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.flat.prior.developmental.noise.marginal.likelihood , sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   packages ="webppl-csv",
#   chains = 1,
#   cores = 1
# )
# 
# read_csv("../../stats/data/llh_child_flat_prior_dev_noise.csv")%>%
#   mutate(model = "flat_prior",
#          parameter = "developmental noise")%>%
#   saveRDS("../../stats/saves/child_ex3_flat_prior_model_developmental_noise_loglike.rds")

@@

child_ex3_flat_prior_model_developmental_noise_likelihood_marginal <- child_ex3_flat_prior_model_developmental_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight),
            ci_lower = hdi_lower(weight),
            ci_upper = hdi_upper(weight))
```

@@

```{r}
# webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.marginal.likelihood, sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   packages ="webppl-csv",
#   chains = 1,
#   cores = 1
# )
# 
# read_csv("../../stats/data/llh_child_prior_only_param_free.csv")%>%
#   mutate(model = "prior_only",
#          parameter = "parameter free")%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model_loglike.rds")

@@

child_ex3_prior_only_model_likelihood_marginal <- child_ex3_prior_only_model_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight),
            ci_lower = hdi_lower(weight),
            ci_upper = hdi_upper(weight))
```

@@

```{r}
# webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.noise.marginal.likelihood, sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   packages ="webppl-csv",
#   chains = 1,
#   cores = 1
# )
# 
# read_csv("../../stats/data/llh_child_prior_only_noise.csv")%>%
#   mutate(model = "prior_only",
#          parameter = "noise")%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")
# 
# child_ex3_prior_only_model_noise_likelihood <- readRDS("../../stats/saves/child_ex3_prior_only_model_noise_loglike.rds")

child_ex3_prior_only_model_noise_likelihood_marginal <- child_ex3_prior_only_model_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight),
            ci_lower = hdi_lower(weight),
            ci_upper = hdi_upper(weight))
```

@@

```{r}
# webppl(
#   program_code = paste(rsaUtils, rsaModel, child.ex3.prior.only.developmental.noise.marginal.likelihood, sep='\n'),
#   data =list(allData = ex3_model_data),
#   data_var = "dataFromR",
#   packages ="webppl-csv",
#   chains = 1,
#   cores = 1
# )
# 
# read_csv("../../stats/data/llh_child_prior_only_dev_noise.csv")%>%
#   mutate(model = "prior_only",
#          parameter = "developmental noise")%>%
#   saveRDS("../../stats/saves/child_ex3_prior_only_model_developmental_noise_loglike.rds")

@@

child_ex3_prior_only_model_developmental_noise_likelihood_marginal <- child_ex3_prior_only_model_developmental_noise_likelihood%>%
  group_by(model,parameter)%>%
  summarise(logP = mean(weight),
            ci_lower = hdi_lower(weight),
            ci_upper = hdi_upper(weight))

@@

# child_ex3_model_comparison <- bind_rows(
#   child_ex3_pragm_model_likelihood_marginal,
#   child_ex3_pragm_model_noise_likelihood_marginal,
#   child_ex3_pragm_model_developmental_noise_likelihood_marginal,
#   child_ex3_flat_prior_model_noise_likelihood_marginal,
#   child_ex3_flat_prior_model_likelihood_marginal,
#   child_ex3_flat_prior_model_developmental_noise_likelihood_marginal,
#   child_ex3_prior_only_model_noise_likelihood_marginal,
#   child_ex3_prior_only_model_likelihood_marginal,
#   child_ex3_prior_only_model_developmental_noise_likelihood_marginal
# )%>%
#   ungroup()%>%
#   mutate(model = reorder(model,logP))%>%
#   saveRDS("../../stats/saves/child_ex3_model_comparison.rds")

@@

#### Means
```{r plot model loglikes ex3 children, include = T}
ggplot(child_ex3_model_comparison, aes(x = model, y = logP, col = model))+
  geom_segment( aes(x=model, xend=model, y=-400, yend=logP), col = "black", size = 1)+
  geom_point(size = 7)+
  #geom_pointrange(aes(x = model, y = logP, ymin = ci_lower, ymax = ci_upper ), pch = 4)+
  theme_few()+ 
  xlab("Model")+
  ylab("Log-likelihood")+
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1))+
  guides(col = F)+
  facet_grid(~parameter)+
  #ylim(-550,-400)+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))

@@

```{r}
# child_ex3_model_ll_dist <- bind_rows(
#   child_ex3_pragm_model_likelihood,
#   child_ex3_pragm_model_noise_likelihood,
#   child_ex3_pragm_model_developmental_noise_likelihood,
#   child_ex3_flat_prior_model_noise_likelihood,
#   child_ex3_flat_prior_model_likelihood,
#   child_ex3_flat_prior_model_developmental_noise_likelihood,
#   child_ex3_prior_only_model_noise_likelihood,
#   child_ex3_prior_only_model_likelihood,
#   child_ex3_prior_only_model_developmental_noise_likelihood
# )%>%
#   ungroup()%>%
#   mutate(model = reorder(model,weight))%>%
#   saveRDS("../../stats/saves/child_ex3_model_comparison_dist.rds")

child_ex3_model_ll_dist <- readRDS("../../stats/saves/child_ex3_model_comparison_dist.rds")

ggplot(child_ex3_model_ll_dist, aes(x = weight, col = model, fill = model))+
  geom_histogram(alpha = .5)+
  facet_wrap(~parameter, scales = "free")+
  theme_few()+
  scale_color_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("pragmatic","prior_only","flat_prior"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))

@@

```{r, include = T}
child_ex3_pragmatic_models_bf <- child_ex3_model_comparison%>%
  filter(model == "pragmatic")%>%
  select(-ci_lower, -ci_upper)%>%
  spread(parameter, logP) %>%
  mutate("dev. noise > noise" = exp(`developmental noise` - noise),
         "noise > parameter free" = exp(noise - `parameter free`),
         "dev. noise > parameter free" = exp(`developmental noise` - `parameter free`)) %>%
  select(-`parameter free`,-`developmental noise`, -noise)

@@

```{r bayes factors ex3 children, include = T}
child_ex3_bf <- child_ex3_model_comparison%>%
  group_by(parameter)%>%
  select(-ci_lower, -ci_upper)%>%
  spread(model, logP) %>%
  mutate("pragmatic > flat_prior" = exp(pragmatic - flat_prior),
         "pragmatic > prior_only" = exp(pragmatic - prior_only),
         "flat_prior > prior_only" = exp(flat_prior - prior_only)) %>%
  select(-pragmatic,-flat_prior, -prior_only)
